\bf Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-15 manuscript/main.tex
d to gamma

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
	Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
	\end{equation*}
	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
Since functional predictors are observed at finitely many discrete time points in practice,
we use finite-dimensional projections obtained by the expansion truncating at $M$ terms.
We choose a moderately large value of $M$ (e.g., 15 or 20) to capture rich functional variation without requiring fine-tuning, as our method promotes smoothness through penalization (see Section~\ref{sec: Regularization of PLS Components}). We denote the truncated space by
	\begin{equation}
		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
	\end{equation}
	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notation for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}
The observations in the hybrid PLS problem can be compactly represented by the tuple
\begin{equation}\label{def:problem_instance}
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	\in
	\mathbb{R}^{(MK+p) \times (MK+p)}
	\times 
	\mathbb{R}^{(MK+p) \times (MK+p)}
	\times
	\mathbb{R}^{n \times (MK+p)}
	\times
	\mathbb{R}^{n}
	,
\end{equation}
defined as follows.
First, let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
\begin{equation}
	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
	\quad
	B^{\prime\prime}_{m, m'} := \int_0^1 b^{\prime\prime}_m(t)\, b^{\prime\prime}_{m'}(t)\, dt,
\end{equation}
for $m, m' = 1, \ldots, M$.
Leveraging these notations, 
we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
\[
\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
\quad \text{and} \quad
\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
\]
We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
\in
\mathbb{R}^{n \times (MK+p)}
$ , and let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.

@@

\begin{proposition}\label{proposition:eigen_noregul}
Let
$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, let
$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
These coefficients are obtained by solving the following generalized eigenvalue problem:
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
\end{equation}

\end{proposition}
Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:linear_noregul}
	We can compute  $\hat{\mathbf{d}}_1, \ldots, \hat{\mathbf{d}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
\begin{equation*}
	\hat{\mathbf{d}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Proofs of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} are provided in Appendix~\ref{section:proof:proposition:linear_noregul_system_unregularized}.
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

@@

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
		\begin{align*}
	\sum \limits_{k=1}^K 
	\lambda_k 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
&=
	\sum \limits_{k=1}^K 
\lambda_k 
\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
\\&	 =
%%%%%%%%%%%%%%%%%%%
	\sum \limits_{k=1}^K 
\lambda_k 
\sum_{l=1}^M
\sum_{m=1}^M
\theta_{ijl} \theta_{ijm}
\int_0^1
 \, b_l^{\prime \prime}(t) 
  b_m^{\prime \prime}(t)
  dt
\\&	 =
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  \sum \limits_{k=1}^K \lambda_k \mathbf{a}^{(k)T} \ddot{J}^{(k)} \mathbf{a}^{(k)} = \xi^{* \top} \Lambda \ddot{J}^\ast \xi^*,
\end{align*}
However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense. As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}. This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness. Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.

\begin{proposition}\label{proposition:eigen_noregul}
	Let
	$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	$
	denote the observed data defined in \eqref{def:problem_instance}.
	At the $l$-th iteration of the PLS algorithm, let
	$( \hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
	These coefficients are obtained by solving the following generalized eigenvalue problem:
	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
		\left(
		\hat{\mathbf{d}}_1^\top, \ldots, \hat{\mathbf{d}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
		\right)^\top
		=
		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
	\end{equation}
	where
	\begin{equation}\label{def:V_matrix}
		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
	\end{equation}

@@

		where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
		\begin{equation}\label{def:Lambda}
			\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
		\end{equation}
		$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

@@

	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \mathbf{d}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\mathbf{d}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}. With the $(MK+p)$-dimensional row vector $\mathbf{d}^* = (\mathbf{d}^{(1)\top}, \ldots, \mathbf{d}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
	\begin{equation}
		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
		\label{eq: rewritten hybrid on scalar regression model}
	\end{equation}

	Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
	\begin{equation}
		\begin{aligned}
			\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
			&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\mathbf{d}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \mathbf{d}^* J^\ast \mathbf{d}^{*T}\right),
		\end{aligned}
		\label{eq: least squares}
	\end{equation}
	where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm. Now taking the derivative of \eqref{eq: least squares} with respect to $\mathbf{d}^*$ and setting the result to zero, we find that  $\mathbf{d}^*$ satisfies the system of linear equations
	\begin{equation*}
		\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \mathbf{d}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
	\end{equation*}
	whose solutions lead to the following estimates of $\mathbf{d}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
	\begin{equation*}
		\widehat{\mathbf{d}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\mathbf{d}}^{*\top}.
	\end{equation*}
	Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.

@@

			For any two tuples $u = (\mathbf{d}_1, \ldots, \mathbf{d}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form

@@

			\langle u, v \rangle_{B} := \sum_{j=1}^K \mathbf{d}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.

@@

	with coefficient vectors $\mathbf{d}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.

@@

		\mathbf{d}_j^\top

>>>>

\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
Given a twice-differentiable basis $\{b_l(t)\}$ of $L^2([0,1])$,
the functional predictors,
the corresponding regression coefficients,
and PLS component direction
 can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t),~
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t), j=1, \ldots, K,~
		%%%%%%%%%%%%%%%%%%%%%%
		\xi 
		=
		\sum_{l=1}^\infty 
		b_l(t)
	\end{equation*}
	At the $l$-th iteration of the PLS algorithm, let
	\begin{equation}
		( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
	\end{equation}

	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
Since functional predictors are observed at finitely many discrete time points in practice,
we use finite-dimensional projections obtained by the expansion truncating at $M$ terms.
We choose a moderately large value of $M$ (e.g., 15 or 20) to capture rich functional variation without requiring fine-tuning, as our method promotes smoothness through penalization (see Section~\ref{sec: Regularization of PLS Components}). We denote the truncated space by
	\begin{equation}
		\mathcal{B} := \operatorname{span} \bigl( b_1(t), \ldots, b_M(t) \bigr).
	\end{equation}
	 We denote the  predictors projected onto $\mathcal{B}$ and the resulting coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notation for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}
The observations in the hybrid PLS problem can be compactly represented by the tuple
\begin{equation}\label{def:problem_instance}
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	\in
	\mathbb{R}^{(MK+p) \times (MK+p)}
	\times 
	\mathbb{R}^{(MK+p) \times (MK+p)}
	\times
	\mathbb{R}^{n \times (MK+p)}
	\times
	\mathbb{R}^{n}
	,
\end{equation}
defined as follows.
First, let $B, B^{\prime\prime} \in \mathbb{R}^{M \times M}$ denote the Gram matrices of the basis functions and their second derivatives, respectively, with entries  
\begin{equation}
	B_{m, m'} := \int_0^1 b_m(t)\, b_{m'}(t)\, dt,
	\quad
	B^{\prime\prime}_{m, m'} := \int_0^1 b^{\prime\prime}_m(t)\, b^{\prime\prime}_{m'}(t)\, dt,
\end{equation}
for $m, m' = 1, \ldots, M$.
Leveraging these notations, 
we define the $(MK + p) \times (MK + p)$ block-diagonal matrices
\begin{equation}\label{def:gram_block}
\mathbb{B} := \operatorname{blkdiag}(B, \ldots, B, I_p)
\quad \text{and} \quad
\mathbb{B}^{\prime\prime} := \operatorname{blkdiag}(B^{\prime\prime}, \ldots, B^{\prime\prime}, I_p),
\end{equation}
We denote $\Theta := (\Theta_1, \ldots, \Theta_K, Z)
\in
\mathbb{R}^{n \times (MK+p)}
$ , and let $\mathbf{y} := (y_1, \ldots, y_n)^\top$ denote the observed response vector.

@@

\begin{proposition}\label{proposition:eigen_noregul}
Let
$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
$
denote the observed data defined in \eqref{def:problem_instance}.
At the $l$-th iteration of the PLS algorithm, let
\begin{equation}
( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top
\end{equation}

denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
These coefficients are obtained by solving the following generalized eigenvalue problem:
\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
	\left(
	\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
	\right)^\top
	=
	\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
	\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
\end{equation}
where
\begin{equation}\label{def:V_matrix}
V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
\end{equation}

\end{proposition}
Since $V$ is a rank 1 matrix, the solution of the generalized eigenvalue problem is easily obtained by matrix multiplication and normalization:
	\begin{proposition} \label{proposition:linear_noregul}
	We can compute  $\hat{\boldsymbol{\gamma}}_1, \ldots, \hat{\boldsymbol{\gamma}}_K$ and $\hat{\boldsymbol{\xi}}$ in Proposition \ref{proposition:eigen_noregul} as 
\begin{equation*}
	\hat{\boldsymbol{\gamma}}_j  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	\Theta_j^\top \mathbf{y},
	\quad
	%%%%%%%%%%%%%%%%
	\hat{\boldsymbol{\xi}}  = \frac{1}{\sqrt{\sum_{j=1}^K 
			\mathbf{y}^\top
			\Theta_j
			B \Theta_j^\top \mathbf{y} 
			+ 
			\mathbf{y}^\top Z Z^\top \mathbf{y}}}
	Z^\top \mathbf{y}.
\end{equation*}
\end{proposition}
The expressions above represent matrix–vector multiplications normalized by a common factor. 
Proofs of Propositions \ref{proposition:eigen_noregul} and \ref{proposition:linear_noregul} are provided in Appendix~\ref{section:proof:proposition:linear_noregul_system_unregularized}.
Although the unnormalized coefficients are computed separately for the functional and scalar part of the PLS component direction, the normalization step couples them, allowing the components to influence each other. This enables the procedure to account for the correlation between functional and scalar components.

@@

One possible approach is to extend smoothed functional PCA \citep{Rice1991} to our optimization problem \eqref{def:maximizer_squared_empirical_cov}, leading to the following formulation:
	\begin{equation*}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\xi}}_{K+1})
	= \arg \max_{\xi \in \mathcal{B}^K \times \mathbb{R}^p,
		\| \xi  \|_\mathcal{H} = 1
	} 
	\biggl\{
	\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)
	- \sum \limits_{j=1}^K \lambda_j 
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	\biggr\}
	,
\end{equation*}
where the smoothing parameters $\{\lambda_j\}_{j=1}^K$ control the trade-off between maximizing covariance and penalizing roughness. Here, the penalization term can be written in matrix form as:
		\begin{align*}
	\sum \limits_{j=1}^K 
	\lambda_j
	\int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
&=
	\sum \limits_{j=1}^K 
\lambda_j
\int_0^1 \bigl\{ \sum_{l=1}^M \theta_{ijl} \, b_l^{\prime \prime}(t) \bigr\}^2 dt
\\&	 =
%%%%%%%%%%%%%%%%%%%
	\sum \limits_{j=1}^K 
\lambda_j
\sum_{l=1}^M
\sum_{m=1}^M
\theta_{ijl} \theta_{ijm}
\int_0^1
 \, b_l^{\prime \prime}(t) 
  b_m^{\prime \prime}(t)
  dt
\\&	 =
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sum \limits_{j=1}^K
\lambda_j
\boldsymbol{\gamma}_j^\top
B^{\prime \prime} 
\boldsymbol{\gamma}_j
%%%%%%%%%%%%%%%%%%%%%%%%%%
\\&= 
\boldsymbol{\xi}^{\top} \Lambda \mathbb{B}^{\prime \prime} \boldsymbol{\xi},
\end{align*}
where we recall that $\mathbb{B}^{\prime \prime} $ is defined in \eqref{def:gram_block}, 
	where $\Lambda \in \mathbb{R}^{(MK+p) \times (MK+p)}$ is defined as
\begin{equation}\label{def:Lambda}
	\Lambda = \mathrm{blkdiag}(\lambda_1 I_M, \cdots, \lambda_K I_M, 0_{p \times p}) , 
\end{equation}
$0_{p \times p}$ denotes a $p \times p$ matrix with all elements equal to zero.

However, the above approach assumes that the functional predictors admit an orthogonal expansion in the $L^2$ sense. As an alternative, we adopt the strategy of \citet{Silverman1996}, which works under weaker conditions than those required by \citet{Rice1991}. This is achieved by replacing the standard orthonormality constraint with one based on a modified inner product that accounts for roughness. Building on this idea, the following proposition reformulates the hybrid PLS problem as a generalized Rayleigh quotient, yielding a smoothed PLS direction that maximizes the squared covariance over a class of smooth functions.

\begin{proposition}\label{proposition:eigen_noregul}
	Let
	$
	(\mathbb{B}, \mathbb{B}^{\prime \prime}, \Theta, \mathbf{y})
	$
	denote the observed data defined in \eqref{def:problem_instance}.
	At the $l$-th iteration of the PLS algorithm, let
	$( \hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top )^\top$
	denote the coefficients of $\hat{\xi}$, defined in \eqref{def:maximizer_squared_empirical_cov},
	which corresponds to the projected unit-norm direction that maximizes the squared empirical covariance.
	These coefficients are obtained by solving the following generalized eigenvalue problem:
	\begin{equation}	\label{eq: Regularized generalized rayleigh quotient equation}
		\left(
		\hat{\boldsymbol{\gamma}}_1^\top, \ldots, \hat{\boldsymbol{\gamma}}_K^\top, \hat{\boldsymbol{\xi}}_{K+1}^\top
		\right)^\top
		=
		\arg \max_{\boldsymbol{\xi} \in \mathbb{R}^{MK+p}}   \boldsymbol{\xi}^\top V \boldsymbol{\xi}
		\quad \text{subject to} \quad \boldsymbol{\xi}^\top \mathbb{B} \boldsymbol{\xi} = 1,
	\end{equation}
	where
	\begin{equation}\label{def:V_matrix}
		V := \frac{1}{n^2} (\mathbb{B} \Theta^\top \mathbf{y})(\mathbb{B} \Theta^\top \mathbf{y})^\top \in \mathbb{R}^{(MK+p) \times (MK+p)},
	\end{equation}

@@

@@

	As in Section \ref{subsec: Step 1: Computing Smoothed PLS components}, the hybrid response can be expanded using basis functions as $\widetilde{W}[\mathbf{t}] = \widetilde{C}^* B^*[\mathbf{t}]$. Similarly, we expand each functional regression coefficient using the basis functions as $\pi^{(k)}(t_k) =\sum_{m=1}^M d_m^{(k)} b^{(k)}_m(t_k) = \boldsymbol{\gamma}^{(k)\top} \mathbf{b}^{(k)}(t_k)$, where $\boldsymbol{\gamma}^{(k)} = (d_1^{(k)}, \ldots, d_M^{(k)})\top \in \mathbb{R}^M$ are basis coefficients. Here, a different basis system can be flexibly chosen to expand the regression coefficient, but without loss of generality we use the same system as in Section \ref{subsec: Step 1: Computing Smoothed PLS components}. With the $(MK+p)$-dimensional row vector $\boldsymbol{\gamma}^* = (\boldsymbol{\gamma}^{(1)\top}, \ldots, \boldsymbol{\gamma}^{(K)\top}, \gamma_1, \ldots, \gamma_p)$ that stacks the basis coefficients and scalar regression coefficients, we can express the linear predictor of the regression as: $\widehat{\boldsymbol{\rho}} \, \boldsymbol{\delta}[\mathbf{t}]^\top = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}]$. Finally, these basis expansions of the hybrid response and the regression coefficient enable us to re-write the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model} in a finite-dimensional form:
	\begin{equation}
		\widetilde{C}^* B^*[\mathbf{t}] = \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] + \mathbf{e}[\mathbf{t}].
		\label{eq: rewritten hybrid on scalar regression model}
	\end{equation}

	Based on the model formulation \eqref{eq: rewritten hybrid on scalar regression model}, we can now formulate the following least squares criterion whose minimizing solution gives the estimate of the regression coefficient $\boldsymbol{\delta}[\mathbf{t}]$ in the hybrid-on-scalar regression model \eqref{eq: hybrid on scalar regression model}:
	\begin{equation}
		\begin{aligned}
			\textnormal{SSE}(\delta) &= \int_\mathcal{T} \left\Vert \,  \widetilde{C}^* B^*[\mathbf{t}] - \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* B^*[\mathbf{t}] \, \right\Vert_F^2 \, d\mathbf{t}  \\
			&= tr\left(\widetilde{C}^{*T}\widetilde{C}^*J^\ast \right) - 2\,tr \left(\boldsymbol{\gamma}^* J^\ast \widetilde{C}^{*T} \widehat{\boldsymbol{\rho}} \right) + tr\left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^* J^\ast \boldsymbol{\gamma}^{*T}\right),
		\end{aligned}
		\label{eq: least squares}
	\end{equation}
	where $tr$ denotes the trace of a matrix, and $\Vert \cdot \Vert_F$ is a Frobenius norm. Now taking the derivative of \eqref{eq: least squares} with respect to $\boldsymbol{\gamma}^*$ and setting the result to zero, we find that  $\boldsymbol{\gamma}^*$ satisfies the system of linear equations
	\begin{equation*}
		\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} \, \boldsymbol{\gamma}^*  J^\ast =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast,
	\end{equation*}
	whose solutions lead to the following estimates of $\boldsymbol{\gamma}^*$ and $\boldsymbol{\delta}[\mathbf{t}]$:
	\begin{equation*}
		\widehat{\boldsymbol{\gamma}}^*  =  \widehat{\boldsymbol{\rho}}^\top  C^* J^\ast \left(\widehat{\boldsymbol{\rho}}^\top \widehat{\boldsymbol{\rho}} J^\ast \right)^{-1} \quad \textnormal{and} \quad \widehat{\boldsymbol{\delta}}[\mathbf{t}] = B^*[\mathbf{t}]^\top \, \widehat{\boldsymbol{\gamma}}^{*\top}.
	\end{equation*}
	Then, we can use $\widehat{\boldsymbol{\delta}}[\mathbf{t}]$ to obtain the subsequent residualized hybrid predictor as $\mathbf{W}_i^{[l+1]}[\mathbf{t}] = \mathbf{W}_i^{[l]}[\mathbf{t}] - \widehat{\boldsymbol{\delta}}_{l}[\mathbf{t}] \widehat{\rho}_{il}$.

@@

			For any two tuples $u = (\boldsymbol{\gamma}_1, \ldots, \boldsymbol{\gamma}_K, \boldsymbol{\zeta})$ and $v = (\mathbf{g}_1, \ldots, \mathbf{g}_K, \boldsymbol{\omega})$ in the product space $(\mathbb{R}^M)^K \times \mathbb{R}^p$, define the bilinear form

@@

			\langle u, v \rangle_{B} := \sum_{j=1}^K \boldsymbol{\gamma}_j^\top B \mathbf{g}_j + \boldsymbol{\zeta}^\top \boldsymbol{\omega}.

@@

	with coefficient vectors $\boldsymbol{\gamma}_j := (d_{j1}, \ldots, d_{jM})^\top \in \mathbb{R}^M$.

@@

		\boldsymbol{\gamma}_j^\top
